### 2019-10-01 190904_Paper_Thesis/Experiments.tex
paper_bdml: new format

\label{chp:Experiments}
..
\section{Data set}
\label{sec:Dataset}
The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was implemented in our experiment to mesure the performance of our proposed system. These are in-house Wi-Fi signature datasets that comprise 980 signatures per direction, as shown in~\ref{tab_dataset}. The size of each sample was 500 x 30 x 6. 
We utilized only the magnitues of the complex values, since the signal have device firmware issues in their phase information~\cite{wang2015understanding}. 
\begin{table}
    \caption{Description of the Dataset.}
    \label{tab_dataset}
    \begin{tabular}{ccc}
    \hline
    Direction of signature & \# of identities & \# of data \\ 
    \hline
    1                      & 98               & 980        \\ 
    2                      & 98               & 980        \\ 
    3                      & 98               & 980        \\ 
    4                      & 98               & 980        \\ 
    \hline
    \end{tabular}
\end{table}

@@

\subsection{Evaluation Scenarios}
%performance
In this paper, the verification performance of the proposed method was evaluated in three ways:
I) In the first experiment, verification performance was compared between the proposed system and other systems including handcraft and deep-learning based methods.
II) Under the second experiments, Comparison of convergence speed was conducted between the proposed system other deep-learning based methods. 
III) The third experiments was conducted to compare the performance degradation between the proposed system and other deep-learning based methods when using a small sized feature vectors. 
In order to compare the feature extraction performance of the proposed system with other deep-learning based methods, we visualized feature space into 2d euclidean space by using PCA. 
% handcraft
We compared the proposed system both with handcraft methods and deep learning based methods.
For handcraft methods, least square estimations (LSE)~\cite{duda2012pattern}, the principal components analysis(PCA)~\cite{turk1991eigenfaces} with LSE, the supprot vector machine~\cite{vapnik2013nature} and the total error minimization with the reduced multivariate polynomal~\cite{toh2003fingerprint,toh2008between} were used. We selected parameters that perform optimally in each handcraft methods. For LSE,SVM and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier Axis. For PCA-LSE, input signature dimension was reduced to 40 following~\cite{moon2017air}. For SVM with Gaussian kernel function (RBF), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$. For TER, parameter M is chosen among $M\in\{1,2,3\}$ and set $\tau=\eta=0.5$ following~\cite{toh2008between}.
For comparison with deep learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
%protocols
The verification performance was evaluated in terms of the Equal Error Rate (EER, \%). We implemented a random 5-runs of 2-fold cross validation tests.
Due to the hardware memory limitations, we used downsized negative pairs according to the number of positive data pairs for calculating the EER. The size of positive data pairs and downsized negative pairs were 18620.

%5.2.2. Parameter settings
\subsection{Parameter Settings}
% KAR structure
For the proposed system, the structure of the KAR learning MLP sub-networks is shown in~\ref{kar_structure}. We empirically chosen two layers size of 1024 and 16. The size of the second layer was equivalent as feature vectors of the proposed ConvNet. The weights in the layers weree initialized as a normal distribution of 0 to 1 before training.
We used $tan^{-1}$ as an active function following~\cite{toh2018analytic}.
\begin{table}[]
    \caption{The network structure of KAR space learning.}
    \label{kar_structure}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500$\times$30$\times$6 &            \\
    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
    Output  & 1$\times$1$\times$50   &            \\ \hline
    \end{tabular}
\end{table}
% conv structure
We used the same ConvNet structure shown in~\ref{conv_structure} and parameter settings for the proposed system and the deep-learning based methods. The CovNet structure consists of 3  convolution filters size of 3$\times$3 and stride 1. A ReLU activation function and 2$\times$2 max-pooling layers is applied between the filters. The depth of each layer was chosen as \{64,128,256\}. The output layer with sigmoid activation was regularized using $L2$ penalty of 0.0001. The size of the final feature vectors was 16.
\begin{table}[]
    \caption{The structure of ConvNet model.}
    \label{conv_structure}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}
% traning parameters
The parameter settings for traning the deep learing network was 
learning rate of 0.0005, the number of iteration as 3000, and set the mini-batch size as 32. We used adam optimatizer for calculating the loss function. We initialized the ConvNet structures following ~\cite{koch2015siamese} before training. For convolution filters, we used a normal distribution of 0 mean and standard deviation of 0.0001. For the biases, parameters for normal distribution was 0.5 mean and standard deviation of 0.01. For calculating triplet loss, we set the alpha value as 0.5.

%5.3. Experimental results
\section{Experimental Results}
%5.3.1. verification performance
\subsection{Performance}
For experiment I,~\ref{tab_performance} shows the average EER from 5-runs of 2-fold cross-validation tests under the optimal parameter settings. As shown in Table~\ref{tab_performance}, the proposed system shows best performance among the handcraft and deep-learning based methods with 19.35\% EER.
Deep learning based methods performed better performance than handcraft methods since they were able to utilize the entire input signal, and their ability to feature extraction were better than handcraft methods.
\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab_performance}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

%roc
As shown in~\ref{fig_roc}, the proposed system also showed the widest Area under ROC curve (AUC).
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
    \caption{Normalized training loss curve.} \label{fig_roc}
\end{figure*}
 %5.3.1. conv speed
~\ref{fig_loss} shows the convergence of the normalized loss function during the training. The convergence speed of the proposed system was the fastest among the deep learning-based methods, meaning that KAR running has accelerated the learning speed.
\subsection{Convergence speed}
 \begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
    \caption{normalized training loss trends} \label{fig_loss}
\end{figure*}
%5.3.2. feature vector
\subsection{Effect of the size of Feature Vector}
- Case3) FC layer
○ Picture
○ The smaller the mapping to a characteristic space, the lower the performance degradation of the proposed method is.
§ Reason 1: Triplet network has better space placement capability than Siamese
Reason 2: Triplet network with KAR learning is better performance

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Size of the Feature Vector & 16    & 8     & 4     & 2     \\ \hline
    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
    Proposed system            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
    \end{tabular}
\end{table}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fclayer_v1.eps}
    \caption{Size of FC layer.} \label{fclayer}
\end{figure}

\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
\end{figure}

>>>>

\label{chp:Experiments}
\section{Data set}
\label{sec:Dataset}
The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was implemented in our experiment to measure the performance of our proposed system. These are in-house Wi-Fi signature datasets that comprise 980 signatures per direction, as shown in~\ref{tab_dataset}. The size of each sample was 500 x 30 x 6. 
\begin{table}
    \caption{Description of the Dataset.}
    \label{tab_dataset}
    \begin{tabular}{ccc}
    \hline
    Direction of signature & \# of identities & \# of data \\ 
    \hline
    1                      & 98               & 980        \\ 
    2                      & 98               & 980        \\ 
    3                      & 98               & 980        \\ 
    4                      & 98               & 980        \\ 
    \hline
    \end{tabular}
\end{table}

@@

\subsection{Evaluation Scenarios}
%performance
In this paper, the verification performance of the proposed method was evaluated in three ways:
I) In the first experiment, verification performance was compared between the proposed system and other systems including handcraft and deep-learning based methods.
II) Under the second experiments, Comparison of convergence speed was conducted between the proposed system other deep-learning based methods. 
III) The third experiments were conducted to compare the performance degradation between the proposed system and other deep-learning based methods when using a small-sized feature vectors. 
To compare the feature extraction performance of the proposed system with other deep-learning based methods, we visualized feature space into 2d euclidean space by using PCA. 
% handcraft
We compared the proposed system both with handcraft methods and deep-learning based methods.
For handcraft methods, least square estimations (LSE)~\cite{duda2012pattern}, the principal components analysis(PCA)~\cite{turk1991eigenfaces} with LSE, the supprot vector machine~\cite{vapnik2013nature} and the total error minimization with the reduced multivariate polynomal~\cite{toh2003fingerprint,toh2008between} were used. We selected parameters that perform optimally in each handcraft methods. For LSE,SVM and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier Axis. For PCA-LSE, input signature dimension was reduced to 40 following~\cite{moon2017air}. For SVM with Gaussian kernel function (RBF), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$. For TER, parameter M is chosen among $M\in\{1,2,3\}$ and set $\tau=\eta=0.5$ following~\cite{toh2008between}.
For comparison with deep-learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
%protocols
The verification performance was evaluated in terms of the Equal Error Rate (EER, \%). We implemented a random 5-runs of 2-fold cross-validation tests.
Due to the hardware memory limitations, we used downsized negative pairs according to the number of positive data pairs for calculating the EER. The size of positive data pairs and downsized negative pairs were 18620.

%5.2.2. Parameter settings
\subsection{Parameter Settings}
% KAR structure
For the proposed system, the structure of the KAR learning MLP sub-networks is shown in~\ref{kar_structure}. We empirically chose two layers size of 1024 and 16. The size of the second layer was equivalent as feature vectors of the proposed ConvNet. The weights in the layers were initialized as a normal distribution of 0 to 1 before training.
We used $tan^{-1}$ as an active function following~\cite{toh2018analytic}.
\begin{table}[]
    \caption{The network structure of KAR space learning.}
    \label{kar_structure}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500$\times$30$\times$6 &            \\
    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
    Output  & 1$\times$1$\times$50   &            \\ \hline
    \end{tabular}
\end{table}
% conv structure
We used the same ConvNet structure shown in~\ref{conv_structure} and parameter settings for the proposed system and the deep-learning based methods. The CovNet structure consists of 3  convolution filters size of 3$\times$3 and stride 1. A ReLU activation function and 2$\times$2 max-pooling layers is applied between the filters. The depth of each layer was chosen as \{64,128,256\}. The output layer with sigmoid activation was regularized using $L2$ penalty of 0.0001. The size of the final feature vectors was 16.
\begin{table}[]
    \caption{The structure of ConvNet model.}
    \label{conv_structure}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}
% traning parameters
The parameter settings for traning the deep learing network was 
learning rate of 0.0005, the number of iteration as 3000, and set the mini-batch size as 32. We used adam optimatizer for calculating the loss function. We initialized the ConvNet structures following ~\cite{koch2015siamese} before training. For convolution filters, we used a normal distribution of 0 mean and standard deviation of 0.0001. For the biases, parameters for normal distribution was 0.5 mean and standard deviation of 0.01. For calculating triplet loss, we set the alpha value as 0.5.

%5.3. Experimental results
\section{Experimental Results}
%5.3.1. verification performance
\subsection{Performance}
For the first experiment,~\ref{tab_performance} shows the average EER from 5-runs of 2-fold cross-validation tests under the optimal parameter settings. As shown in Table~\ref{tab_performance}, the proposed system shows the best performance among the handcraft and deep-learning based methods with 19.35\% EER.
Deep learning based methods performed better performance than handcraft methods since they were able to utilize the entire input signal, and their ability to feature extraction were better than handcraft methods.
\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab_performance}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

%roc
As shown in~\ref{fig_roc}, the proposed system also showed the widest Area under ROC curve (AUC).
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
    \caption{Normalized training loss curve.} \label{fig_roc}
\end{figure*}
 %5.3.1. conv speed
\subsection{Convergence speed}
~\ref{fig_loss} shows the convergence of the normalized loss function during the training. The convergence speed of the proposed system was the fastest among the deep learning-based methods, meaning that KAR running has accelerated the learning speed.
 \begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
    \caption{normalized training loss trends} \label{fig_loss}
\end{figure*}
%5.3.2. feature vector
\subsection{Effect of the size of Feature Vector}
Figure~\ref{fclayer} shows EER for different sizes of feature vectors in the feature space. In general, in metric learning systems, the smaller the size of the feature vectors, the less performance of the system.
From the results, we can see the proposed system shows less performance degradation by a small size feature vector.
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Size of the Feature Vector & 16    & 8     & 4     & 2     \\ \hline
    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
    Proposed system            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
    \end{tabular}
\end{table}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fclayer_v1.eps}
    \caption{Size of FC layer.} \label{fclayer}
\end{figure}
%5.3.3. 2D visualization of feature vector
\subsection{2D visualization of the feature vector}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
\end{figure}
To visualize the performance of feature extraction property of the proposed system, we project the feature space to two-dimensional euclidean space by using PCA in Figs. ~\ref{fig_2d_siam_10},\ref{fig_2d_triKAR_10},\ref{fig_2d_tribase_10}. Through the feature space projected in the 2d euclidean space, we were able to intuitively verify the feature extraction performance of each system by making sure that the point of being close to the space belongs to the same identity. To easily check the distance between points in 2d space, we marked only the first 10 identities.
As shown in the figure, the proposed system used the 2d euclidean space most efficiently. The Siamese network linearly arranged feature vectors, making it difficult to distinguish between classes, and in the case of the baseline triplet network, there were many overlapping areas between identities.

### 2019-10-01 190904_Paper_Thesis/Introduction.tex
paper_bdml: new format

\section{Background}
% signature
Signatures written on paper have long been used as an identification tool, and various methods for verify individuals have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
% biometric
As mobile devices increase, identity verification using biometrics traits is becoming more widely used.
Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convinience and accountability~\cite{hutton2004biometrics}.
% camera sensor
With the development of various sensors such as depth camera and mobile camera, in-air signature have also become available~\cite{bailador2011analysis}. However, they had to use a special sensor prepared for signature. ~\cite{jeon2012system,malik20183dairsig} used depth camera, \cite{ketabdar2012magnetic} used mobile device to record position of hand.
% WiFI CSI
On the other hand, there are studies that use Wi-Fi CSI signals to identify the biometric characteristics of the human body. Since they use commercial devices that are already widespread, they do not need any special input devices.
~\cite{hong2016wfid,liu2015tracking,yousefi2017survey} studied CSI signals to identify the various biometrics characteristics of the body. ~\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to enable users to recognize their gestures.
% CSI signature
Recently, a study was conducted to identify signatures written in the air using CSI signals~\cite{moon2017air}. However, in this study, only the signals entered in one direction were recognized. Due to the nature of the in-air signature, which is difficult to specify the direction in which the signal is input, a verification system is required regardless of the direction in which the signal is entered.
% Deep learning
More recently, there have been studies using deep learning technology to characterize CSI signals. Deep Learning-based models are spotlighted for their automated feature extractors and superior classification capabilities based on them, compared to traditional handcraft models. Deep learning was used to recognize users based on the body shape~\cite{pokkunuru2018neuralwave}, or to identify them with the characteristics shown in their behavior~\cite{shi2017smart}.
% our methods
We used deep learning technology to create a system that can be identity-recognizable even for multi-way air signatures entered with Wi-Fi CSI.
The deep learning model used a triplet network to increase the accuracy of feature extraction while allowing accurate classification, and also improved the model's convergence speed using the kernel and range space running~\cite{toh2018gradient}.

%\newpage
\section{Motivation and Contributions}
...
\newpage
\section{Organization of Thesis}
..

>>>>

\section{Background}
% signature
Signatures written on paper have long been used as an identification tool, and various methods for verifying individuals have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
% biometric
As mobile devices increase, identity verification using biometrics traits is becoming more widely used.
Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convenience, and accountability~\cite{hutton2004biometrics}.
% camera sensor
With the development of various sensors such as depth camera and mobile camera, in-air signature has also become available~\cite{bailador2011analysis}. However, they had to use a special sensor prepared for signature. ~\cite{jeon2012system,malik20183dairsig} used depth camera, \cite{ketabdar2012magnetic} used mobile device to record position of hand.
% WiFI CSI
On the other hand, some studies use Wi-Fi CSI signals to identify the biometric characteristics of the human body. Since they use commercial devices that are already widespread, they do not need any special input devices.
~\cite{hong2016wfid,liu2015tracking,yousefi2017survey} studied CSI signals to identify the various biometrics characteristics of the body. ~\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to enable users to recognize their gestures.
% CSI signature
Recently, a study was conducted to identify signatures written in the air using CSI signals~\cite{moon2017air}. However, in this study, only the signals entered in one direction were recognized. Due to the nature of the in-air signature, which is difficult to specify the direction in which the signal is input, a verification system is required regardless of the direction in which the signal is entered.
% Deep learning
More recently, there have been studies using deep learning technology to characterize CSI signals. Deep Learning-based models are spotlighted for their automated feature extractors and superior classification capabilities based on them, compared to traditional handcraft models. Deep learning was used to recognize users based on the body shape~\cite{pokkunuru2018neuralwave}, or to identify them with the characteristics shown in their behavior~\cite{shi2017smart}.
% our methods
We used deep learning technology to create a system that can be identity-recognizable even for multi-way air signatures entered with Wi-Fi CSI.
The deep learning model used a triplet network to increase the accuracy of feature extraction while allowing accurate classification, and also improved the model's convergence speed using the kernel and range space running~\cite{toh2018gradient}.

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the kernel and the range (KAR) space learning to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
\end{itemize}

\section{Organization of Thesis}
The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference. Our proposed method is discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks are given in Section 5.

### 2019-10-01 190904_Paper_Thesis/Preliminaries.tex
paper_bdml: new format

\label{chp:Preliminary}
..
\section{Biometric Identification System}
\label{sec:Biometrics}
..
\section{Evaluation metrics}
\label{sec:Evaluation}
..
\section{Received Signal Strength Indicator}
\label{sec:RSSI}
..
\section{Channel State Information}
\label{sec:CSI}
..
\subsection{Multiple-Input and Multiple-Output}
\label{sec:MIMO}
..
\section{Shift Matrix}
\label{sec:Shift}
..
\section{Metric Learning}
\label{sec:metric_learning}

>>>>

\label{chp:Survey}

\section{ConvNets}
% description of convnet
Convolutional Neural Networks is a special case of Multi Layer Perceptron and it has unified feature extractor and classifier in one network. It has been widely applied to visual objects such as image, video or 2D array input. Several factors make ConvNets attractive in image-related tasks.
Local connectivity captures local correlation property of the image. It is applicable by using ConvNet filter. Weight sharing helps to reduce the number of weights in feature maps.
Also, CUDA libraries make the training feature maps easier to reduce training time.

%3.3. CSI
\section{Wi-FI Channel State Information}
CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
It runs on a commodity 802.11n NIC and records Channel State Information (CSI based on the 802.11 standards.
The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmitting and receive antennas.
%[From Halperin End]
% Structure of CSI %[From HC's ELM paper]
In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively. The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix. The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
\begin{equation}
    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
\end{equation}
where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
%[From HC's ELM end]
